Uncovering Ferry Traffic Patterns: A Data-Driven Study of Toronto Island Ticket Sales and Redemptions

### 2024-09-27 outputs/paper/paper.qmd
made a very minor change
change from sales to Sales

@fig-linePlot2 shows the Redemption and Sales Counts in months over years. The graph uses dashed lines to represent the monthly sales counts and straight lines for the redemption counts. Notably, the inverted redemption counts are plotted for better visualization alongside the sales data. This figure highlights consistent seasonal patterns, with both ticket sales and redemptions peaking during the summer months, from June to August, across most years. The dip observed in 2020 reflects the significant impact of the COVID-19 pandemic on ferry operations, with reduced ferry usage compared to previous years. These trends show the importance of flexible operational planning to accommodate both predictable seasonal demand and unexpected disruptions.

>>>>

@fig-linePlot2 shows the Redemption and Sales Counts in months over years. The graph uses straight lines to represent the monthly sales counts and dashed lines for the redemption counts. Notably, the inverted sales counts are plotted for better visualization alongside the redemption data. This figure highlights consistent seasonal patterns, with both ticket sales and redemptions peaking during the summer months, from June to August, across most years. The dip observed in 2020 reflects the significant impact of the COVID-19 pandemic on ferry operations, with reduced ferry usage compared to previous years. These trends show the importance of flexible operational planning to accommodate both predictable seasonal demand and unexpected disruptions.
